### 2023-11-30 manuscript.tex
Finished paragraph on alignment figure

\subsection{Signals of conservation are widespread in IDRs}
Having evaluated the statistical properties of the hypothesis testing framework, we next sought to investigate the distribution of significant features across all regions. However, to ensure we would not identify signals of conservation simply as a result of high levels of sequence identity, we restricted our subsequent analyses to disorder regions with a minimum amount of divergence as measured by substitution models (Fig.~\ref{sfig:hierarchy_histogram}). We first quantified the fraction of regions with significant likelihood ratios using the empirical critical values for 1 and 5\% type I error rates, finding that all non-motif features show significance rates that greatly exceed their nominal error rates (Fig.~\ref{fig:conserved}A). The motif features, though, are more variable, with some reaching significance rates similar to those of the non-motif features, whereas many others have rates at or below the nominal values. Generally, the shorter and more degenerate motifs associated with modification sites have higher rates of significance, which may reflect stronger constraints on motifs which are more likely to arise by random mutations. We next calculated the number of significant features in each region using the same critical values. Both yielded highly skewed distributions, indicating the observation of a significant feature increases the probability of observing another significant feature (Fig.~\ref{fig:conserved}B). However, as many features have overlapping definitions, this dependence is expected. To correct for this effect, we therefore randomly shuffled the likelihood ratios between regions for each feature independently and calculated the overall significance rate across all features. For both critical values, the empirical significance rate exceeds the nominal error rate. Taken together, these results indicate constrained feature evolution is widespread in IDRs, with each region containing an average of seven significant features under the 1\% type I error rate.

>>>>

\subsection{Signals of feature conservation are widespread in IDRs}
Having evaluated the statistical properties of the hypothesis testing framework, we next sought to investigate the distribution of significant features across all regions. However, to ensure we would not identify signals of conservation simply as a result of high levels of sequence identity, we restricted our subsequent analyses to disorder regions with a minimum amount of divergence as measured by substitution models (Fig.~\ref{sfig:hierarchy_histogram}). We first quantified the fraction of regions with significant likelihood ratios using the empirical critical values for 1 and 5\% type I error rates, finding that all non-motif features show significance rates that greatly exceed their nominal error rates (Fig.~\ref{fig:conserved}A). The motif features, though, are more variable, with some reaching significance rates similar to those of the non-motif features, whereas many others have rates at or below the nominal values. Generally, the shorter and more degenerate motifs associated with modification sites have higher rates of significance, which may reflect stronger constraints on motifs which are more likely to arise by random mutations. We next calculated the number of significant features in each region using the same critical values. Both yielded highly skewed distributions, indicating the observation of a significant feature increases the probability of observing another significant feature (Fig.~\ref{fig:conserved}B). However, as many features have overlapping definitions, this dependence is expected. To correct for this effect, we therefore randomly shuffled the likelihood ratios between regions for each feature independently and calculated the overall significance rate across all features. For both critical values, the empirical significance rate exceeds the nominal error rate. Thus, constrained feature evolution is widespread in IDRs, with each region containing an average of seven significant features under the 1\% type I error rate.

To illustrate the utility of this method for generating hypotheses to guide the functional dissection of specific proteins, we next compared two regions with elevated values of fraction\_Q and repeat\_QN but different signals of conservation for each (Fig.~\ref{fig:alignment}A-B). Though the alignments of both regions are enriched in glutamine and asparagine residues (Fig.~\ref{fig:alignment}C,E), the first has significant signals of conservation for both features (Fig.~\ref{fig:alignment}D), whereas the second does not (Fig.~\ref{fig:alignment}F). Notably, the first region is from an orthologous group that contains a sequence from the \textit{D. melanogaster} gene {ewg}, which is a transcription factor. As polyglutamine stretches can modulate the activity of transcription factor activation domains, this observation is consistent with the maintenance of an optimal level of transcriptional activation mediated by constraints on glutamine-associated features~\cite{Mitchell1989, Gerber1994}. In contrast, the low likelihood ratios of the second region, whose \textit{D. melanogaster} gene is unannotated, are suggestive of unconstrained glutamine repeat expansion and contraction. Interestingly, this region has highly significant likelihood ratios for several features associated with glycine or phenylalanine repeats despite having few of these residues. However, careful inspection of the alignment reveals several positions where such repeats appear in only one or two sequences, \textit{e.g.} columns 153 and 208. While these strong signals of conservation may represent artifacts of applying a continuous model of trait evolution to features derived from discrete data, they could also indicate true constraints against the presence of flexible or hydrophobic patches in those sequence segments. Taken together, these result highlight the ability of this method to identify biochemical features with signals of constrained evolution while also emphasizing the importance of combining those results with biochemical intuition to suggest plausible hypotheses.
